Nested Sampling with Multiple Objective Functions

### 2018-06-02 doc/ms.tex
Pose the question about the NS measure

\section{Properties of Nested Sampling}
What is special about the NS sequence of distributions?

Consider the Nested Sampling measure, proportional to the amount of time
NS spends in each region of the space. Since NS moves at a constant rate
in terms of $\log(X)$, this measure is
\begin{align}
m_{\rm NS} &\propto \frac{\pi(\xx)}{X(\xx)}.
\end{align}

>>>>

\section{Unique Properties of Nested Sampling}
What is special about the NS sequence of distributions?

Consider the Nested Sampling measure, proportional to the amount of time
NS spends in each region of the space. Since NS moves at a constant rate
in terms of $\log(X)$, this measure is proportional to
\begin{align}
m_{\rm NS} &\propto \frac{\pi(\xx)}{X(\xx)}.\label{eqn:measure}
\end{align}
The sequence of dead particles emitted by NS is then used to compute properties
of the posterior distribution, or other canonical distributions for temperatures
other than 1. Why does this work? Why does the NS measure of
Equation~\ref{eqn:ns_measure} allow the user to get a reasonable number of
samples for {\em any} canonical distribution?
